### 2023-02-13 article.tex
Remove 'rowcolors'
Put example text in italics

\begin{verbatim}
We compared the in-blood concentrations of IL6RA 
between subjects having AA versus subjects having GG at SNP rs12133641,
using an unpaired one-tailed T-test,
as we expect the average concentration of IL6RA for those with AA 
to be less than the average concentration in those with GG.
\end{verbatim}

@@

\iffalse
\rowcolors{2}{gray!10}{gray!40}
\begin{table}[h]
  \begin{tabular}{|p{2cm}|l|}
    \hline
    \textbf{Type of code} & \textbf{Recommendation} \\
    \hline
    No code       & Disallow papers that do not supply code publicly \\
    \hline
    Raw code      & Don't publish raw code as text, host it on a code hosting website \\
    \hline
    Hosted code   & Use a standarized badge for build status \\
                  & Use a standarized badge for code coverage \\
                  & Standardize to link between paper and code host \\
    \hline
    Runnable code & Allow to upload containers without limits \\
                  & Website to host containers must allow for annotation \\
                  & Use a standarized badge for the container to be functioning  \\
                  & Standarize to link between container, paper and code repository \\
    \hline
  \end{tabular}
  \caption{Recommendations described in this paper}
  \label{tab:recommendations}
\end{table}
\fi

>>>>

\textit{
We compared the in-blood concentrations of IL6RA 
between subjects having AA versus subjects having GG at SNP rs12133641,
using an unpaired one-tailed T-test,
as we expect the average concentration of IL6RA for those with AA 
to be less than the average concentration in those with GG.
}

@@

\iffalse
\begin{table}[h]
  \begin{tabular}{|p{2cm}|l|}
    \hline
    \textbf{Type of code} & \textbf{Recommendation} \\
    \hline
    No code       & Disallow papers that do not supply code publicly \\
    \hline
    Raw code      & Don't publish raw code as text, host it on a code hosting website \\
    \hline
    Hosted code   & Use a standarized badge for build status \\
                  & Use a standarized badge for code coverage \\
                  & Standardize to link between paper and code host \\
    \hline
    Runnable code & Allow to upload containers without limits \\
                  & Website to host containers must allow for annotation \\
                  & Use a standarized badge for the container to be functioning  \\
                  & Standarize to link between container, paper and code repository \\
    \hline
  \end{tabular}
  \caption{Recommendations described in this paper}
  \label{tab:recommendations}
\end{table}
\fi
